Blame and Coercion: Together Again for the Second Time

### 2019-10-17 paper.tex
fully remove abbrev NC
name LazyD inefficient CEK as D

@@

	\caption{Dynamic semantics of the cast calculi as a CEK machine ($ 
	\mathcal{C} $)}
	\label{machine-cekc}
\end{figure}

@@

\figref{fig:applyCast-D-C} defines the $ applyCast $ for \lazyD. 
We conjecture that with this $ applyCast $, the CEK machine in 
\figref{machine-cekc} would agree with the \lazyD{} cast calculus in 
\citet{siek2009exploring}. We denote this \lazyD{} machine by $ 
\mathcal{C}_{\mathtt{D}} $.

@@

\begin{figure}
	\[
	\begin{array}{rclr}
	\stxrule{I}{injectable types (\lazyD)}{
		\POOfun{T}{T}}
	\stxrule{I}{injectable types (\lazyUD)}{
		\POOfun{\TOOdyn}{\TOOdyn}
	}
	\stxrule{c}{coercions}{
		\ncInj{I} \mid
		\ncProj{I}{l} \mid
		\ncId \mid
		\ncFail{l} \mid
		\ncSeq{c}{c} \mid
		\ncFun{c}{c}
	}
	\stxrule{\bar{c}}{wrapper coercions}{	
		\ncInj{I} \mid
		\ncFun{\hat{c}}{\hat{c}} \mid
		\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}}
	}
%	\stxrulecont{
%		\ncProd{\hat{c}}{\hat{c}} \mid
%		\ncSeq{\ncProd{\hat{c}}{\hat{c}}}{\ncInj{I}} \mid
%		\ncSum{\hat{c}}{\hat{c}} \mid
%		\ncSeq{\ncSum{\hat{c}}{\hat{c}}}{\ncInj{I}} \mid	
%	}
	\stxrule{\hat{c}}{normal coercions}{
		\bar{c} \mid
		\ncId \mid
		\ncFail{l} \mid
		\ncProj{I}{l} \mid
		\ncSeq{\ncProj{I}{l}}{\ncFail{l}} \mid
		\ncSeq{\ncProj{I}{l}}{\ncInj{I}}
	}
	\stxrulecont{
		\ncSeq{\ncProj{I}{l}}{\ncFun{\hat{c}}{\hat{c}}} \mid
		\ncSeq{\ncProj{I}{l}}{\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}}}
	}
	\end{array}
	\]
	\caption{Syntax of Normal Coercion (NC)}
	\label{fig:normal-coercion}
\end{figure}

@@

\subsection{All Surely \lazyD{} and Monoidic Cast Representations Respect 
$\mathcal{D}$}

@@

We use bisimulation to proof equivalence between the two machines.
\todo[inline]{Which two machines? -JS}
The bisimulation relation of states ($\eqvDS{C}{s}{s}$) is mostly derived from 
the definitions of $ \mathcal{D} $. Exceptions include the relations from 
continuations to pre-continuations, between continuations, and between values. 
We omit subscripts when there is no ambiguity.

@@

\begin{lemma}[Weak Bisimulation between $ \mathcal{S}(\cdot) $ and $ 
	\mathcal{D} $]
	\label{thm:surely-monoidic-reduce}
	For all cast representations $ C $, 
	if $ C $ is surely \lazyD{} and monoidic,
	$ s_1 \in \mathcal{D} $,
	$ s_2 \in \mathcal{S}(C) $, and
	$ s_1 \approx s_2 $, 
	\begin{enumerate}
		\item If $ \judgeCreduce{s_1}{s_3} $,
		then
		there exist $ s_5 \in \mathcal{D} $, $ s_4 \in \mathcal{S}(C) $,
		such that \begin{itemize}
			\item $ s_5 \approx s_4 $, and
			\item $ \judgeSreduce{C}{s_2}{s_4} $,
			\item $ \judgeCreduceTrans{s_3}{s_5} $
		\end{itemize}
		\item If $ \judgeSreduce{C}{s_2}{s_4} $,
		then
		there exist $ s_3 \in \mathcal{D} $,
		such that \begin{itemize}
			\item $ s_3 \approx s_4 $
			\item $ \judgeCreduceTrans{s_1}{s_3} $
		\end{itemize}
	\end{enumerate}
\end{lemma}
\begin{proof}
	See the supplementary material.
\end{proof}

\begin{lemma}[Surely \lazyD\ and Monoidic Cast Representations Respect 
	$ \mathcal{D} $]
	\label{thm:surely-monoidic-eval}
	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is surely 
	\lazyD{} and monoidic,
	\[
	\judgeCeval{e}{o} \; \text{if and only if} \; 
	\judgeSeval{C}{e}{o}
	\]
\end{lemma}
\begin{proof}
  Immediately from Lemma~\ref{thm:surely-monoidic-reduce}.
  \todo[inline]{I'm guessing that you prove this lemma by induction,
    using Lemma~\ref{thm:surely-monoidic-reduce}.
    Proofs by induction are not ``immediate''. -JS}
\end{proof}

\subsection{\lazyD\ Hyper-coercion Respect $ \mathcal{D} $}
\label{sec:LDHC-correct}

@@

\begin{theorem}[\lazyD{} hypercoercion Respect $ \mathcal{D} $]
	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ 
	\[
	\judgeCeval{e}{o} \; \text{if and only if} \; 
	\judgeSeval{H}{e}{o}
	\]
\end{theorem}
\begin{proof}
	Immediately from Lemma~\ref{thm:surely-monoidic-eval},
	Lemma~\ref{thm:hc-surely-lazyD}, and 
	Proposition~\ref{thm:hc-monoid}.
\end{proof}

@@

\begin{theorem}[Surely \lazyD\ Cast Representations Respect 
	$ \mathcal{D} $]
	\label{thm:surely-lazyD-correct}
	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is surely 
	\lazyD{}
	\[
	\judgeCeval{e}{o} \; \text{if and only if} \; 
	\judgeSeval{C}{e}{o}
	\]
\end{theorem}
\begin{proof}
	Immediately from Lemma~\ref{thm:surely-monoidic-eval} and 
	Proposition~\ref{thm:surely-lazyD-eqv}.
\end{proof}

>>>>

% names
\newcommand{\ineffCEK}{$ \mathcal{C} $}
\newcommand{\ineffCEKD}{$ \mathcal{D} $}
\newcommand{\ineffCEKUD}{$ \mathcal{UD} $}
\newcommand{\judgeDreduce}[2]{#1 \longrightarrow_{\mathcal{D}} #2}
\newcommand{\judgeDreduceTrans}[2]{#1 \longrightarrow_{\mathcal{D}}^{*} #2}
\newcommand{\judgeDeval}[2]{#1 \Downarrow_{\mathcal{D}} #2}
\newcommand{\effCEK}[1]{$ \mathcal{S}(#1) $}

@@

	\caption{Dynamic semantics of the cast calculi as a CEK machine}
	\label{machine-cekc}
\end{figure}

@@

\figref{fig:applyCast-D-C} defines the $ applyCast $ for \lazyD. 
We conjecture that with this $ applyCast $, the CEK machine in 
\figref{machine-cekc} would agree with the \lazyD{} cast calculus in 
\citet{siek2009exploring}. We denote this \lazyD{} machine by \ineffCEKD{},
and the corresponding relations by $ \judgeDreduce{s}{s} $, $ 
\judgeDreduceTrans{s}{s} $, and $ \judgeDeval{e}{o} $

@@

\begin{figure}
	\[
	\begin{array}{rclr}
	\stxrule{I}{injectable types (\lazyD)}{
		\POOfun{T}{T}}
	\stxrule{I}{injectable types (\lazyUD)}{
		\POOfun{\TOOdyn}{\TOOdyn}
	}
	\stxrule{c}{coercions}{
		\ncInj{I} \mid
		\ncProj{I}{l} \mid
		\ncId \mid
		\ncFail{l} \mid
		\ncSeq{c}{c} \mid
		\ncFun{c}{c}
	}
	\stxrule{\bar{c}}{wrapper coercions}{	
		\ncInj{I} \mid
		\ncFun{\hat{c}}{\hat{c}} \mid
		\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}}
	}
%	\stxrulecont{
%		\ncProd{\hat{c}}{\hat{c}} \mid
%		\ncSeq{\ncProd{\hat{c}}{\hat{c}}}{\ncInj{I}} \mid
%		\ncSum{\hat{c}}{\hat{c}} \mid
%		\ncSeq{\ncSum{\hat{c}}{\hat{c}}}{\ncInj{I}} \mid	
%	}
	\stxrule{\hat{c}}{normal coercions}{
		\bar{c} \mid
		\ncId \mid
		\ncFail{l} \mid
		\ncProj{I}{l} \mid
		\ncSeq{\ncProj{I}{l}}{\ncFail{l}} \mid
		\ncSeq{\ncProj{I}{l}}{\ncInj{I}}
	}
	\stxrulecont{
		\ncSeq{\ncProj{I}{l}}{\ncFun{\hat{c}}{\hat{c}}} \mid
		\ncSeq{\ncProj{I}{l}}{\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}}}
	}
	\end{array}
	\]
	\caption{Syntax of Normal Coercion}
	\label{fig:normal-coercion}
\end{figure}

@@

\subsection{All Surely \lazyD{} and Monoidic Cast Representations Respect 
$\mathcal{C}_{\mathtt{D}}$}

@@

We use bisimulation to proof equivalence between the two machines.
\todo[inline]{Which two machines? -JS}
The bisimulation relation of states ($\eqvDS{C}{s}{s}$) is mostly derived from 
the definitions of $ \mathcal{C} $. Exceptions include the relations from 
continuations to pre-continuations, between continuations, and between values. 
We omit subscripts when there is no ambiguity.

@@

\begin{lemma}[Weak Bisimulation between $ \mathcal{S}(\cdot) $ and $ 
	\mathcal{C} $]
	\label{thm:surely-monoidic-reduce}
	For all cast representations $ C $, 
	if $ C $ is surely \lazyD{} and monoidic,
	$ s_1 \in \mathcal{C} $,
	$ s_2 \in \mathcal{S}(C) $, and
	$ s_1 \approx s_2 $, 
	\begin{enumerate}
		\item If $ \judgeCreduce{s_1}{s_3} $,
		then
		there exist $ s_5 \in \mathcal{C} $, $ s_4 \in \mathcal{S}(C) $,
		such that \begin{itemize}
			\item $ s_5 \approx s_4 $, and
			\item $ \judgeSreduce{C}{s_2}{s_4} $,
			\item $ \judgeCreduceTrans{s_3}{s_5} $
		\end{itemize}
		\item If $ \judgeSreduce{C}{s_2}{s_4} $,
		then
		there exist $ s_3 \in \mathcal{C} $,
		such that \begin{itemize}
			\item $ s_3 \approx s_4 $
			\item $ \judgeCreduceTrans{s_1}{s_3} $
		\end{itemize}
	\end{enumerate}
\end{lemma}
\begin{proof}
	See the supplementary material.
\end{proof}

\begin{lemma}[Surely \lazyD\ and Monoidic Cast Representations Respect 
	$ \mathcal{C} $]
	\label{thm:surely-monoidic-eval}
	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is surely 
	\lazyD{} and monoidic,
	\[
	\judgeCeval{e}{o} \; \text{if and only if} \; 
	\judgeSeval{C}{e}{o}
	\]
\end{lemma}
\begin{proof}
  Immediately from Lemma~\ref{thm:surely-monoidic-reduce}.
  \todo[inline]{I'm guessing that you prove this lemma by induction,
    using Lemma~\ref{thm:surely-monoidic-reduce}.
    Proofs by induction are not ``immediate''. -JS}
\end{proof}

\subsection{\lazyD\ Hyper-coercion Respect $ \mathcal{C}_\mathtt{D} $}
\label{sec:LDHC-correct}

@@

\begin{theorem}[\lazyD{} hypercoercion Respect $ \mathcal{C}_\mathtt{D} $]
	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ 
	\[
	\judgeCeval{e}{o} \; \text{if and only if} \; 
	\judgeSeval{H}{e}{o}
	\]
\end{theorem}
\begin{proof}
	Immediately from Lemma~\ref{thm:surely-monoidic-eval},
	Lemma~\ref{thm:hc-surely-lazyD}, and 
	Proposition~\ref{thm:hc-monoid}.
\end{proof}

@@

\begin{theorem}[Surely \lazyD\ Cast Representations Respect 
	$ \mathcal{C}_\mathtt{D} $]
	\label{thm:surely-lazyD-correct}
	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is surely 
	\lazyD{}
	\[
	\judgeCeval{e}{o} \; \text{if and only if} \; 
	\judgeSeval{C}{e}{o}
	\]
\end{theorem}
\begin{proof}
	Immediately from Lemma~\ref{thm:surely-monoidic-eval} and 
	Proposition~\ref{thm:surely-lazyD-eqv}.
\end{proof}
